%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{John}{de Vera}{
\location{\qquad \qquad \qquad \qquad \quad \qquad \qquad  }
\begin{center}

I'm an engineer who loves solving problems. I'm excited about data and the development of software with machine learning.\\
......................................................................................................................................................................................................................................................................\\

Email: \href{mailto:john.devera@gmail.com}{john.devera@gmail.com}  | 
Mobile: +1-604-780-3484 \\
Website: \href{http://www.johndevera.com}{johndevera.com} ||
GitHub: \href{http://www.github.com/johndevera}{github.com/johndevera} |
LinkedIn: \href{http://www.linkedin.com/in/johndevera/}{linkedin.com/in/johndevera}
\end{center}


}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.35\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Toronto}
\descript{Masters of Mechanical Engineering}
\location{Certificate: Mechatronics \& Robotics}
\location{Certificate: Advanced Manufacturing}
\location{Graduation: May 2018 (expected)}
\location{Toronto, ON, Canada}
\location{GPA: 3.83}
\sectionsep

\subsection{BCIT Aerospace}
\descript{Diploma in Aircraft Avionics}
\location{Graduation: August 2016}
\location{Richmond, BC, Canada}
\location{GPA: 91\% with Distinction}
\sectionsep

\subsection{University of British Columbia}
\descript{Bachelors of Electrical Engineering}
\location{Graduation: May 2012}
\location{Vancouver, BC, Canada}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

%\iffalse %begin of comment code
\subsection{Software Development}
- Python | C | C++ | Java | Unix | LaTeX \\
- Machine Learning \\
- Probabilistic Models \\
%- Logistic Regression | Naive Bayes |\\ K-Means | CNN | KNN | MOG | SVM \\
- Keras | Theano | TensorFlow \\
- Natural Language Processing \\
- Sentiment Analysis \\
- Watson Data Analytics \\
- Web Scraping \\
- Object Oriented Programming \\
- IDEs: Eclipse | Anaconda \\
%- GitHub
\sectionsep
%\fi %end of comment code


\iffalse %begin of comment code
\subsection{Manufacturing}
- Lean Six Sigma \\
- TPM | 5S \\
- Continuous Improvement \\
- Preventative Maintenance \\
- Process Improvement \\
- Operations Management \\
- Leadership | Supervision \\
- Electrical Wiring \\
- Supply Chain \\
- Production Scheduling \\
\sectionsep
\fi %end of comment code


%\iffalse %begin of comment code
\subsection{Electrical Engineering}
Circuit Analysis \\
Analog and Digital Circuits \\
Wiring Diagrams \\
Soldering \\
Radio Theory \\
Function Generator \\
Digital Multimeter\\ 
\sectionsep
%\fi %end of comment code

\iffalse %begin of comment code
\subsection{Avionics}
Circuit Analysis \\
Analog and Digital Circuits \\
AC Wiring Diagrams \\
Soldering \\
Antenna/Radio Theory \\
Systems Troubleshooting \\
Electrical Harness Design \\
Navigation Systems \\
Function Generator \\
Digital Multimeter\\ 
\sectionsep
\fi %end of comment code


%\iffalse %begin of comment code
\section{TA Experience}
%\subsection{Software}
- Organizational Design (2018 expected) \\
- Electronics for Robotics (2017) \\
- Electrical and Circuit Analysis (2016) \\
- Introduction to C Programming (2010) \\
\sectionsep
%\fi %end of comment code



\iffalse %begin of comment code
\section{Achievements}
- BCIT Graduating Achievement Award for Leadership and Teamwork (2016) \\
- BCIT Award for Distinction (2016) \\
- PepsiCo TPM and Lean Six Sigma (2013) \\
- APEGBC Engineer-in-Training (2012) \\
- French Proficiency - 5wk Immersion (2008)\\
\fi %end of comment code

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.61\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    ACADEMIC COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic Coursework}

%\iffalse
\runsubsection{Robotics/Mechatronics}
\descript{| Machine Learning}
%\descript{}
%\location{Machine Learning}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize} 
\item Developed Deep Learning Neural-Nets in Python using Keras, in both Theano and TensorFlow backends.
\item Processed ML datasets: MNIST, Toronto Faces, Flickr Dataset, S\&P500 stock prices.
\item Experience with various ML classifiers such as: Logistic Regression, Naive Bayes, Stochastic Variational Inference, KNN, CNN, K-Means, MOG, and SVM.
\item Used IBM Watson Analytics for Natural Language Processing.
\item Performed Web-scraping and Sentiment Analysis on web pages.
\item Integrated NVIDIA CUDA GPU with computer using cuDNN toolkit to improve learning rates.
\end{tightemize}
\sectionsep
%\fi

\iffalse
\runsubsection{Advanced Manufacturing}
\descript{}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize} 
\item Used data analysis techniques to perform preventative maintenance on heavy machinery.
\item Used Systems Engineering fundamentals and best practices at a high level of implementation.
\item Researched the impact of Artificial Intelligence in Manufacturing and the impact on Operations Management.
\end{tightemize}
\sectionsep
\fi

\iffalse
\runsubsection{Aircraft Avionics}
\descript{| AME-E}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize} 
\item Work experience accreditation from Transport Canada.
\item Knowledge of Canadian Aviation Regulations (CARs).
\item Performed maintenance tasks on various jet aircraft including Boeing 737 and Bombardier CRJ200.
\item Performed bench testing of various electrical components.
\item Installed NAVCOM system on Bell 206A Helicopter
\item Created electrical wiring harnesses and routed it through aircraft.
\item Performed bench and operational testing on various VHF and UHF COM/NAV and GPS TX and RX.
\item Conducted all installations and tests IAW A/C electrical wiring diagrams and mechanical system schematics using various AMMs and CMMs.
\
\end{tightemize}
\sectionsep
\fi


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}

%Software and Engineering Based
%\iffalse
\runsubsection{PepsiCo}
\descript{| Production Engineer, Operations and Maintenance}
\location{June 2012 - March 2015 | Vancouver and Calgary, Canada}
%\location{June 2012 - March 2013 | Vancouver, BC, Canada}
%\location{February 2013 - March 2015 | Calgary, AB, Canada}
\begin{tightemize} 
\item Developed internal reporting tools to monitor product outputs and system outages in real time. Tech stack used: Java and Unix scripting.
\item Developed a nightly process, which parsed logs and consolidated other data files to generate executive summaries on output and efficiencies.
\item Organized big data collection projects to analyze large amounts of data on machine downtime and to present findings and possible improvements to management.
\end{tightemize}
\sectionsep
%\fi

%Long, Operations and Manufacturing Based
\iffalse
\runsubsection{PepsiCo}
\descript{| Production Engineer, Operations and Maintenance}
\location{June 2012 - March 2015 | Vancouver and Calgary, Canada}
%\location{June 2012 - March 2013 | Vancouver, BC, Canada}
%\location{February 2013 - March 2015 | Calgary, AB, Canada}
\begin{tightemize} 
\item Recruited for PepsiCo's Operations Leadership Program (OLP), class of 2012.
\item Supervised a workforce of 34 machine operators on the production line on various shifts.
\item Analyzed key workflow efficiencies and downtime through cost.
\item Developed and led TPM program and initiatives for line OEE improvement.
\item Liaised directly with Maintenance Engineering, Production, Quality Control, and Contractors/Suppliers.
\item Led incident review board which tracks issues and reports to senior management on costs, delays, and root causes.
\item Achieved second-highest rating across all North American facilities for machine retrofit program.
\item Authored the requirements specification and user documentations for training and on boarding new users.
\item Conducted appropriate product and safety trainings with employees. 
\item Updated work processes for audit compliance with provincial and federal HSE requirements and ISO 22000.
\item Presented to senior Canadian directors on the requirements spec for operator onboarding and job training certification.
\end{tightemize}
\sectionsep
\fi
%Short, Operations and Manufacturing Based
\iffalse
\runsubsection{PepsiCo}
\descript{| Production Engineer, Operations and Maintenance}
\location{June 2012 - March 2015 | Vancouver and Calgary, Canada}
%\location{June 2012 - March 2013 | Vancouver, BC, Canada}
%\location{February 2013 - March 2015 | Calgary, AB, Canada}
\begin{tightemize} 
\item Recruited for PepsiCo's Operations Leadership Program (OLP), class of 2012.
\item Supervised a workforce of 34 machine operators on the production line on various shifts.
\item Liaised directly with Maintenance Engineering, Production, Quality Control, and Contractors/Suppliers.
\item Led incident review board which tracked issues and reported on costs, delays, and root causes to senior management.
\item Wrote the requirements specification and user documentation for training and on boarding new users.
\item Updated work processes for audit compliance with provincial / federal HSE requirements and ISO22000.training certification.
\end{tightemize}
\sectionsep
\fi

%\iffalse
\runsubsection{Epic Data}
\descript{| Software Developer Intern}
\location{June 2009 - August 2009 | Richmond, BC, Canada}
\begin{tightemize} 
\item Developed a GUI on a multi-purpose terminal (MPT).
\item Designed and implemented an authentication algorithm in Java that uses 4-bit and 8-bit binary number combinations to verify embedded key codes within the security password of a user ID badge.
\item Wrote test cases to debug the programmer-developed code. 
%\item Drafted GUI user documentation.
\end{tightemize}
\sectionsep
%\fi

\iffalse
\item Developed a GUI for technicians running a multi-purpose terminal (MPT).
\item Designed and implemented an authentication algorithm in Java that uses 4-bit and 8-bit binary number combinations to verify embedded key codes within the security password of a user ID badge.
\item Wrote test cases to debug the programmer-developed code. 
\item Drafted the user documentation that accompanied the GUI.
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\runsubsection{Programming and Machine Learning}
\begin{tightemize} 
\item Compared Recurrent Neural Networks and Gaussian Processes in predicting stock price movements, achieving an accuracy of 79 on a specific stock.
%\item Analyzed Canada's perception around the world during its 150th Anniversary by using various data gather and analysis techniques such as web-scraping, sentiment analysis, and Natural Language Processing.
\item Currently developing in Java a fully functional Poker table simulation. This incorporates objects such as players and all actions such as betting and decision analysis. Plan is to incorporate machine learning and reinforcement learning.
\end{tightemize} 

\end{minipage} 
\end{document}  \documentclass[]{article}